%-------------------------
% Resume in Latex
% Updated for Vishal Rajput
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section format
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\achievementItem}[1]{\item\small{#1 \vspace{-6pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\justify \begin{itemize} \vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Vishal Rajput} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9644272681 ~ 
    \raisebox{-0.2\height}\faEnvelope\ \href{mailto:vishalrajput15817@gmail.com}{vishalrajput15817@gmail.com} ~ 
    \raisebox{-0.2\height}\faLinkedin\ \href{https://linkedin.com/in/vishal-rajput-7b421a203}{linkedin.com/in/vishal-rajput} ~
    \raisebox{-0.2\height}\faGithub\ \href{https://github.com/1235vishal}{github.com/1235vishal} ~
    \raisebox{-0.2\height}\faGlobe\ \href{https://vishdev1235.netlify.app}{vishdev1235.netlify.app}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
Final-year Computer Science student and \textbf{Full Stack Developer} with global freelancing experience in building and deploying scalable web applications. Skilled in React.js, Node.js, Express.js, MySQL, and MongoDB with expertise in UI/UX design, deployment, and payment integrations. Experienced in delivering complete end-to-end development solutions from design to deployment.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {AKP Build And Gain Pvt Ltd}{Oct 2023 -- Present}
  {Full Stack Development Engineer I (Contract)}{Remote}
  \resumeItemListStart
    \resumeItem{Delivered \textbf{5+ client web platforms} including booking apps, dashboards, and corporate sites.}
    \resumeItem{Built a \textbf{PG rent management \& billing system} with Razorpay integration, reducing manual effort by 70\%.}
    \resumeItem{Optimized backend APIs and databases, improving response speed by 40\%.}
  \resumeItemListEnd

\resumeSubheading
  {Freelance Full Stack Developer}{2022 -- Present}
  {Independent}{Worldwide Remote}
  \resumeItemListStart
    \resumeItem{Worked on multiple areas: \textbf{Figma design}, \textbf{frontend \& backend development}, \textbf{production deployments}, and payment gateway integration.}
    \resumeItem{Delivered complete end-to-end solutions for clients across industries using React.js, Node.js, Express, MySQL, and MongoDB.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{PG Booking Website} $|$ \emph{React, Node.js, Express, MySQL, Razorpay} $|$ \href{https://shivshaktipg.com}{shivshaktipg.com}}{}
    \resumeItemListStart
      \resumeItem{Users can \textbf{book PGs online}, owners can \textbf{list/manage PGs \& tenants}, with integrated billing \& payments.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Acharya Brahaspati Trust} $|$ \emph{React, Node.js, Express, Razorpay} $|$ \href{https://acharyabrahaspatitrust.org}{acharyabrahaspatitrust.org}}{}
    \resumeItemListStart
      \resumeItem{NGO platform for \textbf{blogs, events, online classes, and donations} supporting cultural initiatives.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Trisect Global} $|$ \emph{React, Node.js, Express, MySQL} $|$ \href{https://trisectglobal.com}{trisectglobal.com}}{}
    \resumeItemListStart
      \resumeItem{Recruitment company website showcasing services \& industries with candidate database integration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Lakshmi Narain College of Technology \& Science}{2022 -- 2026}
    {B.Tech – Computer Science \& Engineering}{Bhopal, India}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
    \textbf{Languages:} JavaScript, Java, SQL \\
    \textbf{Frameworks \& Libraries:} React.js, Node.js, Express.js, REST APIs \\
    \textbf{Databases:} MySQL, MongoDB \\
    \textbf{Tools \& Platforms:} Git/GitHub, Vercel, Netlify, cPanel, aPanel, Render, Figma \\
    \textbf{Other Skills:} UI/UX Design, Deployment, Payment Integrations
  }
\end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in]
  \achievementItem{Handled diverse freelancing work: \textbf{Figma design}, \textbf{frontend/back-end development}, and \textbf{production deployments} for global clients.}
  \achievementItem{\textbf{Salesforce Developer (Agentblazer Champion Certified)}.}
  \achievementItem{Built solutions reducing client operational workload by up to 60\%.}
\end{itemize}

\end{document}
